How are galaxies assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering

### 2017-03-06 text/ms.tex
Ref. Report Minor #1 addressed. @MJV Double check correction.

In this work, we aim to investigate the dependence of halo occupation on halo concentration, and how this dependence can be constrained in the low-redshift universe with the measurements of the 2PCF of galaxies with a wide range of luminosities in the SDSS DR7 main galaxy sample. 
In order to achieve this goal, we need to adopt a HOD model that takes into account 
a dependence on halo properties beyond mass. There are a number of frameworks in the literature. \citet{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} have proposed environment-dependent HOD modeling methods that take into account the large-scale density contrast. The model that we use in this investigation is the decorated HOD framework (\citealt{decorated}). In the decorated HOD framework, at a fixed halo mass, halos are populated with galaxies according to the standard HOD modeling. Then, a secondary halo property is selected. At a fixed halo mass, halos are split into two populations: halos with the highest and halos with the lowest values of the secondary property. The two population receive enhancements (decrements) in their number of galaxies according to a assembly bias amplitude parameter. The assembly bias parameter will not be degenerate with the rest of the HOD parameters.

>>>>

%In this work, we aim to investigate the dependence of halo occupation on halo concentration, and how this dependence can be constrained in the low-redshift universe with the measurements of the 2PCF of galaxies with a wide range of luminosities in the SDSS DR7 main galaxy sample. 
%%% CHH: Re-phrasing 
In this work, we aim to investigate the dependence of halo occupation on 
{\bf \color{dred} 
    halo concentration and how this dependence can be constrained in the low-redshift universe by 2PCF measurements of galaxies in a wide range of luminosities in the SDSS DR7 main galaxy sample. 
}
%%%
In order to achieve this goal, we need to adopt a HOD model that takes into account 
a dependence on halo properties beyond mass. 
%%% CHH: Re-phrasing to address ref. report
{\bf \color{dred} 
    A number of frameworks in the literature \citep{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} 
    have proposed environment-dependent HOD models that take into account the large-scale density contrast. 
    In this investigation, we use the following case of the decorated HOD framework \citep{decorated}.  
    In our decorated HOD framework, at fixed halo mass, halos are populated with galaxies according to 
    the standard HOD model. Then using a secondary halo property, halos are split into two populations
    in halo mass bins: halos with the highest and lowest secondary property values. Afterwards, based
    on the assembly bias amplitude parameter, the number of galaxies in the two populations are enhanced
    or reduced. In this model, the assembly bias parameter is not be degenerate with the rest of the HOD 
    parameters. 
}
%%%
